\Large \includegraphics[height=\baselineskip]{title.png} \\ \vspace{0.65mm} \large \normalfont CSE 227: Computer Security - Spring 2017 \\ \textit{ University of California San Diego }

### 2017-06-14 docs/paper.tex
Draft of everything except Conclusions

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,url,epsfig,endnotes}
\providecommand{\keywords}[1]{\textbf{\textit{Keywords:}} #1}

@@

\abstract{
The introduction of Internationalized Domain Names made access the web easier to non-English speakers.
However, it also opened the possibility of using homograph domain names maliciously.
We analyzed the potential impact of this type of attack, commonly referred to as IDN homograph attack.
Our approach was based on clustering internationalized domain names with their counterparts in the Alexa Top 1m web sites ranking.
The results obtained indicate that there are more than a thousand (at least) IDN homographs among \textit{.com} domains.
Most of them are not being used actively, but they still posses a potential security risk as there are no guarantees they will remain inactive in the future.
}

@@

\section{Introduction}
Domain names were originally designed to only support ASCII characters.
Internationalized Domain Names (IDNs) were proposed back in December 1996 by Martin D\"{u}rst\endnote{\url{https://tools.ietf.org/html/draft-duerst-dns-i18n-00}} for the purpose of letting non-English speakers use Internet without additional restrictions.
This extension involves representing Unicode characters in ASCII using Punycode, so that they could be then rendered back into their Unicode representation.
Homograph letters (different letters whose representation is almost, if not, the same), however, present a potential security vulnerability.
For example, Cyrillic letter ``a'' can look identical to Latin letter ``a'' depending on the font.
In other languages, like Chinese, there exists many homograph letters between traditional Chinese and simplified Chinese.
Malicious attackers could then register a domain where one of the letters is actually Cyrillic but whose representation matched a Latin one.
Users could be linked to this newly registered malicious page, and they may not have any visual indication (at least without further interaction) that the page is not the one they think they are visiting.

@@

\section{Background}
This section summarizes different mechanisms used to defend against internationalized domain name homograph attack.
There are two mayor players trying to prevent this kind of attack, browsers and TLDs.
Browsers, on the client side, display the non-Unicode version of the domain name based on different white-lists and restrictions.
TLDs, on the other side, have different policies on domain name registrations to try to restrict the use of homographs.
A more comprehensive study would be required for other possible attack vectors, such as email clients.

@@

\subsection{Top-Level Domains}
TODO
- What does different TLDs do
- ccTLDs

The Internet Corporation for Assigned Names and Numbers(ICANN) is responsible for the management of domain name system. In 2009, ICANN started to accept the application for internationalized country code top-level domain(IDN ccTLD) for the benefits of non-English speaking people and the first IDN ccTLD was added to DNS root zone in 2010\ref{tld1}.

ICANN is aware of the potential vulnerability of homograph attacks and limits the usage of letter that is similar to Latin. For any application of potential IDN ccTLD, if there exists letter that is similar to an existing TLD, ICANN may reject them, especially for two-letter TLD. Three-letter TLD have higher chance to be accepted, as they are considered to be safer than two-letter TLD. ICANN listed detailed checking process in the Final Implementation Plan\ref{icann}.

For the second level domains, some registrant registers similar IDNs for brand protection, like Google. Google has registered most IDN in 2005.

@@

@@

The two high level categories that were defined are \textit{Canonical} and \textit{Third Party}.
The first one, \textit{Canonical}, was employed when the domain is registered by the same organization as its canonical homograph domain name.
The second one, \textit{Third Party}, was used when the domain is registered by a different organization than its canonical homograph domain name.
Additionally, a more detailed classification was made:
\itemize{
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\item \textit{Canonical - Parking}: domain was registered but it was not accessible via HTTP.
\item \textit{Canonical - Redirect}: domain redirected (HTTP Status Code 301/307/308) to its canonical homograph domain name.
\item \textit{Third Party - Redirect to Canonical:} domain redirected (HTTP Status Code 301/307/308) to its canonical homograph domain name.
\item \textit{Third Party - Unrelated}: domain resolved, but the contents of the website were totally unrelated to its canonical homograph domain name.
\item \textit{Third Party - Parking}: domain was registered, but it was not accessible via HTTP, or when accessed, a default domain parking web page was displayed.
\item \textit{Third Party - Scam}: domain resolved, and the website displayed was a clear attempt (similar color, logos, etc.) to make users think they were visiting the canonical homograph domain name.
}

% TODO: Align tables

\begin{table*}[]
\centering
\begin{tabular}{lrr}
\hline
Domains                                           & \#                         & \%                         \\ \hline
\itshape\sffamily{Canonical domain names}         & \itshape\sffamily{458731}  & \itshape\sffamily{8.31\%}  \\
\hspace{0.5cm} With IDN homographs                & 825                        & 6.04\%                     \\
\hspace{0.5cm} Without IDN homographs             & 457906                     & 2.27\%                     \\
\itshape\sffamily{Internationalized Domain Names} & \itshape\sffamily{1045400} & \itshape\sffamily{91.69\%} \\
\hspace{0.5cm} With canonical homograph           & 1099                       & 3.68\%                     \\
\hspace{0.5cm} Without canonical homograph        & 1044301                    & 2.74\%                     \\ \hline
\end{tabular}
\caption{Overview of the clustering results.}
\label{clustering-results}
\end{table*}

\begin{table}[]
\centering
\begin{tabular}{lr}
\hline
Domain       & \# of IDN homographs \\ \hline
google.com   & 24                   \\
youtube.com  & 3                    \\
facebook.com & 9                    \\
baidu.com    & 3                    \\
yahoo.com    & 4                    \\
reddit.com   & 1                    \\
qq.com       & 2                    \\
taobao.com   & 1                    \\
live.com     & 1                    \\
vk.com       & 6                    \\ \hline
\end{tabular}
\caption{Top ten .com domains in the Alexa ranking with IDN homographs.}
\label{top-com-alexa-with-idns}
\end{table}

@@

\section{Results}

We obtained 458731 domain names from the \textit{top domains snapshot} that belonged to the \texttt{.com} zone.
From the \textit{.com snapshot}, we identified a total of 1044301 internationalized domains.
However, only a low percentage of the internationalized domain names (3.68\%) had a matching homograph canonical domain name in the \textit{top domains snapshot}.
Even if we take into account that our homograph detection algorithm is rather limited (as described before), these results still indicate that the majority of internationalized domain names are not being used in homograph attacks.
An overview of these clustering results can be found in Table~\ref{clustering-results}.

Table~\ref{top-com-alexa-with-idns} shows the number of internationalized domain name homographs for the top ten \texttt{.com} domains.
It is worth noting that most of the homograph domains of \textit{google.com} are actually registered by Google, possibly as a defensive measure.
Another surprising result of the homograph clustering is that 81.87\% of the groups have just one homograph internationalized domain name.
This suggests that this kind of attack may not be targeted only to top websites, but rather to any domain where valuable information could be obtained from the users by a scam.

@@

>>>>

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,url,epsfig,endnotes,dblfloatfix}
\providecommand{\keywords}[1]{\textbf{\textit{Keywords:}} #1}

@@

\abstract{
The introduction of Internationalized Domain Names made access the web easier to non-English speakers.
However, it also opened the possibility of using homograph domain names maliciously.
We analyzed the potential impact of this type of attack, commonly referred to as IDN homograph attack.
Our approach was based on clustering internationalized domain names with their counterparts in the Alexa Top 1m web sites ranking.
The results obtained indicate that there are more than a thousand (at least) IDN homographs among \textit{.com} domains.
While most of them are not being used actively, they still possess a potential security risk as there are no guarantees they will remain inactive in the future.
}

@@

\section{Introduction}
Domain names were originally designed to only support ASCII characters.
Internationalized Domain Names (IDNs) were proposed back in December 1996 by Martin D\"{u}rst\endnote{\url{https://tools.ietf.org/html/draft-duerst-dns-i18n-00}} for the purpose of letting non-English speakers use Internet without additional restrictions.
This extension involves representing Unicode characters in ASCII using Punycode, so that they could be then rendered back into their Unicode representation.
Homograph letters (different letters whose representation is almost, if not, the same), however, present a potential security vulnerability.
For example, Cyrillic letter ``a'' can look identical to Latin letter ``a'' depending on the font.
In other languages, like Chinese, there exist many homograph letters between traditional Chinese and simplified Chinese.
Malicious attackers could then register a domain where one of the letters is actually Cyrillic but whose representation matched a Latin one.
Users could be linked to this newly registered malicious page, and they may not have any visual indication (at least without further interaction) that the page is not the one they think they are visiting.

@@

\section{Background}
This section summarizes different mechanisms used to defend against internationalized domain name homograph attack.
There are two major players trying to prevent this kind of attack, browsers and TLDs.
Browsers, on the client side, display the non-Unicode version of the domain name based on different white-lists and restrictions.
TLDs, on the other side, have different policies on domain name registrations to try to restrict the use of homographs.
A more comprehensive study would be required for other possible attack vectors, such as email clients.

@@

\subsection{ICANN and TLD Registrars}
The Internet Corporation for Assigned Names and Numbers (ICANN) is the organization responsible for the management of domain name system.
In 2009, ICANN started to accept applications for internationalized country code top-level domains (IDN ccTLDs).
The first IDN ccTLD was added to DNS root zone in 2010~\cite{mac2010}.
ICANN is aware of the potential security risk that homograph attacks pose, and limits the usage of Latin-look-alike letters.
They may reject applications for IDN ccTLDs if there exists an existing TLD that looks similar to the one being petitioned for.
The detailed checking process is defined in their ``Final Implementation Plan for IDN ccTLD Fast Track Process''~\cite{icann2013}.

Most second level registrars do not have a explicit public policy to prevent the registration of homograph domains.
Only a few have implemented restrictions to eliminate this potential risk.
For instance, \texttt{.cn}, \texttt{.biz}, \texttt{.hk}, and all Chinese TLDs will simultaneously activate both traditional and simplified Chinese IDNs once one of them is registered.

@@

\begin{table*}[b!]
\centering
\begin{tabular}{lrr}
\hline
Domains                                           & \#                         & \%                         \\ \hline
\itshape\sffamily{Canonical domain names}         & \itshape\sffamily{458731}  & \itshape\sffamily{8.31\%}  \\
\hspace{0.5cm} With IDN homographs                & 825                        & 6.04\%                     \\
\hspace{0.5cm} Without IDN homographs             & 457906                     & 2.27\%                     \\
\itshape\sffamily{Internationalized Domain Names} & \itshape\sffamily{1045400} & \itshape\sffamily{91.69\%} \\
\hspace{0.5cm} With canonical homograph           & 1099                       & 3.68\%                     \\
\hspace{0.5cm} Without canonical homograph        & 1044301                    & 2.74\%                     \\ \hline
\end{tabular}
\caption{Overview of the clustering results.}
\label{clustering-results}
\end{table*}

@@

The two high level categories that were defined are \textit{Canonical} and \textit{Third Party}.
The first one, \textit{Canonical}, was employed when the domain is registered by the same organization as its canonical homograph domain name.
The second one, \textit{Third Party}, was used when the domain is registered by a different organization than its canonical homograph domain name.
Additionally, a more detailed classification was made:
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\item \textit{Canonical - Parking}: domain was registered but it was not accessible via HTTP.
\item \textit{Canonical - Redirect}: domain redirected (HTTP Status Code 301/307/308) to its canonical homograph domain name.
\item \textit{Third Party - Redirect to Canonical:} domain redirected (HTTP Status Code 301/307/308) to its canonical homograph domain name.
\item \textit{Third Party - Unrelated}: domain resolved, but the contents of the website were totally unrelated to its canonical homograph domain name.
\item \textit{Third Party - Parking}: domain was registered, but it was not accessible via HTTP, or when accessed, a default domain parking web page was displayed.
\item \textit{Third Party - Scam}: domain resolved, and the website displayed was a clear attempt (similar color, logos, etc.) to make users think they were visiting the canonical homograph domain name.
\end{itemize}

\section{Results}
We obtained 458731 domain names from the \textit{top domains snapshot} that belonged to the \texttt{.com} zone.
From the \textit{.com snapshot}, we identified a total of 1044301 internationalized domains.
However, only a low percentage of the internationalized domain names (3.68\%) had a matching homograph canonical domain name in the \textit{top domains snapshot}.
Even if we take into account that our homograph detection algorithm is rather limited (as described before), these results still indicate that the majority of internationalized domain names are not being used in homograph attacks.
An overview of these clustering results can be found in Table~\ref{clustering-results}.

\begin{table}[!ht]
\centering
\begin{tabular}{lr}
\hline
Domain       & \# of IDN homographs \\ \hline
google.com   & 24                   \\
youtube.com  & 3                    \\
facebook.com & 9                    \\
baidu.com    & 3                    \\
yahoo.com    & 4                    \\
reddit.com   & 1                    \\
qq.com       & 2                    \\
taobao.com   & 1                    \\
live.com     & 1                    \\
vk.com       & 6                    \\ \hline
\end{tabular}
\caption{Top ten .com domains in the Alexa ranking with IDN homographs.}
\label{top-com-alexa-with-idns}
\end{table}

@@

Table~\ref{top-com-alexa-with-idns} shows the number of internationalized domain name homographs for the top ten \texttt{.com} domains.
It is worth noting that most of the homograph domains of \textit{google.com} are actually registered by Google, possibly as a defensive measure.
Another surprising result of the homograph clustering is that 81.87\% of the groups have just one homograph internationalized domain name.
This suggests that this kind of attack may not be targeted only to top websites, but rather to any domain where valuable information could be scammed from users.

@@

\clearpage
